BOLD Parameter Estimation Using Particle Filters

### 2010-07-24 doc/thesis/particlefilters.tex
some changes to the abstract

Initially the particles will have the same output, $0$, however, as $u(t)$
changes, the response of each particle to that input will result in different
outputs. Particles that have a $v_{yi}$ near $V_y$ will be weighted higher,
and others farther away will be weighted lower. As the particle filter
runs, weights will compound resulting in a distribution that asymptotically
approaches the true joint distribution of the $X(t)$.  Of course, as I
mentioned in \autoref{sec:Particle Filter Resampling}, particles weighted 
zero do not significantly
contribute to the empirical distribution, so re-sampling may be necessary.

>>>>

Initially the particles will have the same output, $0$, however, as $u(t)$
changes, the response of each particle to that input will result in different
outputs. Particles that have a $v_{yi}$ near $V_y$ will be weighted higher,
and others farther away will be weighted lower. As the particle filter
runs, weights will compound converging to a distribution that asymptotically
approaches the true joint distribution of the $X(t)$.  As I
mentioned in \autoref{sec:Particle Filter Resampling}, particles with 
weights approaching zero do not significantly
contribute to the empirical distribution, so re-sampling will be necessary.

### 2010-07-24 doc/thesis/thesis.tex
some changes to the abstract

Abstract Abstract Abstract ...

>>>>

Traditional methods of analyzing FMRI images use a linear combination of
just a few static regressors. This works demonstrates an alternative
approach using a physiologically inspired nonlinear model. By using a 
particle filter to optimize the model parameters, the computation time
is kept reasonable without requiring a linearization of the noise in the state
variables. The activation results show regions similar those found in 
SPM; however, there are some notable regions not detected by 
SPM. Though the parameters selected by the particle filter based approach
are more than sufficient to predict the BOLD response,
more model constraints are needed to uniquely identify a single set
of parameters. This ill-posed nature explains the large discrepancies
found in other research that attempted to characterize the model parameters.
For this reason the final distribution of parameters is more medically relevant
than a single estimate. Because the output of the particle filter is 
a full posterior probability, the reliance on the mean to estimate 
parameters is not strictly necessary. This work presents
not just a viable alternative to the traditional method of detecting
activation, but an extensible technique of estimating the joint BOLD
parameter distribution.
